The \dealii{} Library, Version 9.2

### 2020-06-01 9.2/paper.tex
More edits.

  \item \texttt{step-70} solves a fluid structure interaction problem on
        non-matching parallel distributed triangulations, showing the usage of
        the \texttt{particles::ParticleHandler} class for two different tasks:
        i) to track the position of quadrature points of a non-matching
        solid grid immersed in a fluid grid, and ii) to track the position of a
        collection of massless tracers.

        In \texttt{step-70} we consider a mixing problem in the laminar flow
        regime. Such problems occur in a wide range of applications ranging
        from chemical engineering to power generation (e.g. turbomachinery).
        Mixing problems are particularly hard to solve numerically, because
        they often involve a container (with fixed boundaries, and possibly
        complex geometries such as baffles), and one (or more) immersed and
        rotating impellers, making it difficult to use Arbitrary Lagrangian
        Eulerian formulations, where the fluid domain – along with the mesh! –
        is smoothly deformed to follow the deformations of the immersed solid.
        We show how to solve such problems using a penalization technique
        where the flow problem is solved in the union of the fluid and solid
        domain, and the movement of the solid is imposed weakly using a
        Nitsche-like penalization.

        The \texttt{particles::ParticleHandler} class is used in this context
        to allow integration of the fluid basis functions on the solid domain
        (which is immersed and non-matching w.r.t. the fluid grid). This is
        achieved by attaching the information required to perform the
        integration on the solid grid, to the property field of the particles
        associated with the quadrature points of the solid, and advecting those
        particles according to the solid velocity. In this program, we assign
        the solid velocity externally, and we do not solve for it, even though
        the program can be easily extended to allow for the solution of
        coupled elasticity equations on the solid domain.
\end{itemize}

>>>>

  \item \texttt{step-70} solves a fluid structure interaction problem on
        non-matching parallel distributed triangulations, showing the usage of
        the \texttt{particles::ParticleHandler} class for two different tasks:
        (i) to track the position of quadrature points of a non-matching
        solid grid immersed in a fluid grid, and (ii) to track the position of a
        collection of massless tracers.

        The program considers a mixing problem in the laminar flow
        regime. Such problems occur in a wide range of applications ranging
        from chemical engineering to power generation (e.g. turbomachinery).
        Mixing problems are particularly hard to solve numerically, because
        they often involve a container (with fixed boundaries, and possibly
        complex geometries such as baffles), and one (or more) immersed and
        rotating impellers, making it difficult to use Arbitrary Lagrangian
        Eulerian formulations, where the fluid domain – along with the mesh! –
        is smoothly deformed to follow the deformations of the immersed solid.
        We show how to solve such problems using a penalization technique
        where the flow problem is solved in the union of the fluid and solid
        domain, and the movement of the solid is imposed weakly using a
        Nitsche-like penalization.

        The \texttt{particles::ParticleHandler} class is used in this context
        to allow integration of the fluid basis functions on the solid domain
        (which is immersed and non-matching with regard to the fluid grid). This is
        achieved by attaching the information required to perform the
        integration on the solid grid, to the property field of the particles
        associated with the quadrature points of the solid, and advecting those
        particles according to the solid velocity. In this program, we
        externally prescribe rather than solve for the
        the solid velocity; however,
        the program can easily be extended to allow for the solution of
        coupled elasticity equations on the solid domain.
\end{itemize}
